The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-09 SC-challenge.tex
chose alternate paragraph on software review

Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
Journals accepting ``software'' submissions (e.g., \textit{F1000Research}, \textit{SoftwareX}, \textit{Computer Physics Communications}) can conflate review of the submitted software with a review of research output \textbf{produced by} the software. \katznote{this really isn't the case for SoftwareX - it has a process for review of software itself (\url{https://www.elsevier.com/__data/assets/pdf_file/0010/97066/ReviewerForm.pdf}), and the papers it accepts are software paper, not research (science) output papers.  Maybe we need some different examples.}
The rOpenSci community represents one exception to this, with a documented review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci collection.

\katznote{potential alt paragraph}
Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
Some journals that accept both ``software'' submissions and general research papers can conflate review of the submitted software with a review of research output \textbf{produced by} the software. Software-only journals (e.g., \textit{Journal of Open Research Software}, \textit{SoftwareX}), and the
rOpenSci community represent exceptions to this, with documented review processes. For example, rOpenSci has a process \cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci collection.

>>>>

Finally, on the topic of peer review of software, there is a distinct lack of standardization around the practices of peer review.
Some journals that accept both ``software'' submissions and general research papers can conflate review of the submitted software with a review of research output \textbf{produced by} the software.
Software-only journals (e.g., \textit{Journal of Open Research Software}, \textit{SoftwareX}) and the rOpenSci community represent exceptions to this, with documented review processes.
For example, rOpenSci has a process \cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci collection.
